Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-11 article.tex
There are approx 460 epitopes in original and 448 in recent proteome

\paragraph{Extracting polypeptides}

@@

>>>>

\paragraph{Gene prediction}

@@

For gene prediction, we used \richel{X} as is recommended
in a recent benchmark study for eukaryotes (\cite{scalzitti2020benchmark}).

Although the closed source Vgas (\cite{zhang2019vgas}) appears promising,
we opted for reproducible research and used Prodigal (\cite{hyatt2012gene})
instead, which was just a bit better than prokka (\cite{seemann2014prokka}).
